### 2021-11-25 sections/conferences-full.tex
Update conferences-full.tex

\item{\small González-Bustamante, B. (2021). {\itshape Methodological Challenges and Innovations in the Study of Elites}. Presentation XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2021). {\itshape R Applications in Social Sciences: Data Mining and Economic Modelling}. Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2021). {\itshape Data Mining, Modelling and Machine Learning Applications for Social Sciences}. Presentation delivered at the I Workshop of the Training Data Lab, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Evolution and early governmental responses to COVID-19 in South America}. Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape New Approaches to Studying Political Elites}. Presentation delivered at the Colloquium of the Observatório de Elites, Universidade Federal do Paraná, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}. Presentation delivered at the Seminar Cycle on Human Rights in Latin America, Virtual.}\vspace{1mm} %% Sergipe, Brazil

\item{\small González-Bustamante, B. (2020). {\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}. Presentation delivered at the PRS Workshop Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2018). {\itshape Cabinet Stability and Turnover from a Multilevel Approach}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Cisternas, C. (2018). {\itshape Social Network Analysis: Application for Elites Study}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Geospatial Analysis of Partisanship Density and Electoral Turnout: Evidence from the Chilean Case}. Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, González.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2018). {\itshape Survival of Ministers and Vice-Ministers in Chile: Stability and Turnover from a Multilevel Approach}. Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics, Curitiba, Brazil.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Del Valle, N. (2017). {\itshape Media Pluralism and Digital Media Public Opinion}. Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A. (2017). {\itshape Revolving Door? Analysis of Public-Private Circulation in Chile}. Presentation delivered at the II Foreign Affairs Meeting, Santiago, Chile.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Joignant, A. (2016). {\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Joignant, A., \& González-Bustamante, B. (2016). {\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C. (2016). {\itshape Analysis of the Academic Production on Open Government in Spanish}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). {\itshape Revolving Door and Public-Private Circulation in Chile}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities, Santiago, Chile.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Barría, D. (2016). {\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}. Presentation delivered at the IX Chilean Congress of Sociology, Talca, González.}\vspace{1mm}

@@

\item{\small Cisternas, C., \& González-Bustamante, B. (2016). {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}. Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times, Santiago, Chile.}\vspace{1mm}

@@

\item{\small Olivares, A., \& González-Bustamante, B. (2015). {\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}. Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}

\item{\small Garrido-Vergara, L., \& González-Bustamante, B. (2015). {\itshape Elites and Political Reforms: The Chilean Case}. Presentation delivered at the International Congress of Elites and Leadership, Salamanca, Spain.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2014). {\itshape Chilean Elections 2013: Incumbency, Campaign Spending, and Electoral Success in the Congress}. Presentation delivered at the Research Colloquium of the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Digital Independent Media in Chile}. Presentation delivered at the Seminar of Mass Media Pluralism in Chile, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape The Governmental Political Elite in Chile}. Presentation delivered at the Seminar of Elites Studies in Chile, Santiago, Chile.}\vspace{1mm}

>>>>

\item{\small González-Bustamante, B. (2021). {\itshape Methodological Challenges and Innovations in the Study of Elites}. Presentation delivered at the XLV Annual Conference of the Brazilian National Association of Graduate Studies and Research in Social Sciences, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2021). {\itshape R Applications in Social Sciences: Data Mining and Econometric Modelling}. Presentation delivered at the Political Science Method Lecture at the Universidad de Chile, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2021). {\itshape Data Mining, Modelling and Machine Learning Applications for Social Sciences}. Presentation delivered at the I Training Data Lab Workshop, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Evolution and Early Governmental Responses to COVID-19 in South America}. Presentation delivered at the Workshop of the School of Political Science and Public Administration at the Universidad de Talca, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape New Approaches to Studying Political Elites}. Presentation delivered at the Colloquium of the Observatório de Elites at the Universidade Federal do Paraná, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2020). {\itshape Protest and Social Unrest in Latin America: Determinants and Critical Junctures}. Presentation delivered at the Seminar Cycle on Human Rights in Latin America at the Universidade Tiradentes, Virtual.}\vspace{1mm} %% Sergipe, Brazil

\item{\small González-Bustamante, B. (2020). {\itshape Critical Events and Ministerial Turnover in Latin American Presidential Democracies}. Presentation delivered at the PRS DPhil in Politics Workshop in Hilary Term at the University of Oxford, Oxford, UK.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2018). {\itshape Cabinet Stability and Turnover from a Multilevel Approach}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Cisternas, C. (2018). {\itshape Social Network Analysis: Application for Elites Study}. Presentation delivered at the Symposium of Political-Administrative Elites: Planning a Research Agenda at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2018). {\itshape Geospatial Analysis of Partisanship Density and Electoral Turnout: Evidence from the Chilean Case}. Presentation delivered at the XIII Chilean Congress of Political Science, Santiago, Chile.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2018). {\itshape Survival of Ministers and Vice-Ministers in Chile: Stability and Turnover from a Multilevel Approach}. Presentation delivered at the International Symposium of Ministers and Ministries: Technocracy and Politics at the Universidade Federal do Paraná, Curitiba, Brazil.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Del Valle, N. (2017). {\itshape Media Pluralism and Digital Media Public Opinion}. Presentation delivered at the III Seminar of Pluralism and Mass Media in Chile at the Universidad Alberto Hurtado, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B., Maillet, A., \& Olivares, A. (2017). {\itshape Revolving Door? Analysis of Public-Private Circulation in Chile}. Presentation delivered at the II Foreign Affairs Meeting at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Joignant, A. (2016). {\itshape Gaps and Elite-Mass Congruence in Chile and Uruguay}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

\item{\small Joignant, A., \& González-Bustamante, B. (2016). {\itshape Family Ties in the Senate and the Chamber of Deputies, Chile from 1989 to 2014}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

\item{\small Barría, D., González-Bustamante, B., \& Cisternas, C. (2016). {\itshape Analysis of the Academic Production on Open Government in Spanish}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). {\itshape Revolving Door and Public-Private Circulation in Chile}. Presentation delivered at the Seminar of Political, Economic, and Intellectual Elites: Gaps and Inequalities at the Universidad de Santiago, Santiago, Chile.}\vspace{1mm}

@@

\item{\small González-Bustamante, B., \& Barría, D. (2016). {\itshape Production Patterns of the Contemporary Knowledge in Social Sciences}. Presentation delivered at the IX Chilean Congress of Sociology, Talca, Chile.}\vspace{1mm}

@@

\item{\small Cisternas, C., \& González-Bustamante, B. (2016). {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}. Presentation delivered at the International Seminar of Social Sciences at the Crossroad: Latin American Intellectuals and Technocrats in Authoritarianism Times at the Universidad Bernardo O'Higgins, Santiago, Chile.}\vspace{1mm}

@@

\item{\small Olivares, A., \& González-Bustamante, B. (2015). {\itshape Survival of Ministers and Undersecretaries in Chile (1990-2014)}. Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}

\item{\small Garrido-Vergara, L., \& González-Bustamante, B. (2015). {\itshape Elites and Political Reforms: The Chilean Case}. Presentation delivered at the International Congress of Elites and Leadership at the Universidad  de Salamanca, Salamanca, Spain.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2014). {\itshape Chilean Elections 2013: Incumbency, Campaign Spending, and Electoral Success in the Congress}. Presentation delivered at the Centre for Political Analysis and Research Colloquium, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Digital Independent Media in Chile}. Presentation delivered at the Seminar of Mass Media Pluralism in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape The Governmental Political Elite in Chile}. Presentation delivered at the Seminar of Elites Studies in Chile at the Centre for Political Analysis and Research, Santiago, Chile.}\vspace{1mm}
